---
title: "Midterm Project"
author: "Ziyu Jin"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    #number_sections: yes
    theme: cosmo
    toc: yes
    toc_depth: 3
    toc_float: yes
  # pdf_document: 
  #   latex_engine: xelatex
  
---

```{r setup, include=FALSE}
# Prepare the environment
knitr::opts_chunk$set(
	fig.width = 8.5,
	message = FALSE,
	warning = FALSE,
	# include = FALSE,
	echo = FALSE
)

options(tinytex.verbose = TRUE)

# Clear environment of variables and functions
rm(list = ls(all = TRUE)) 

# Clear environment of packages
if(is.null(sessionInfo()$otherPkgs) == FALSE) {
  lapply(paste("package:", names(sessionInfo()$otherPkgs), sep=""), 
         detach, character.only = TRUE, unload = TRUE)
}
```


```{r, warning=FALSE, message=FALSE}
# Load Packages
#install.packages("lpSolve")
#install.packages("lpSolveAPI")
library(lpSolve)
library(lpSolveAPI)
#library(tidyverse)
`%>%` <- magrittr::`%>%`
library(knitr)
library(kableExtra)
library(igraph)
```


# Q1 Network Map
```{r}
# Data matrix, could also import data file
seer <- matrix(nc = 2, byrow = TRUE, 
              c(1, 3, 
                1, 4, 
                1, 5,
                1, 6,
                1, 7,
                1, 8,
                2, 3, 
                2, 4,
                2, 5,
                2, 6,
                2, 7,
                2, 8,
                3, 9, 
                3, 10, 
                3, 11, 
                4, 9, 
                4, 10,
                4, 11,
                5, 9, 
                5, 10,
                5, 11,
                6, 9, 
                6, 10,
                6, 11,
                7, 9, 
                7, 10,
                7, 11,
                8, 9, 
                8, 10,
                8, 11)) 

# Make graph by setting 7 nodes/vertices, edges from nodes/vertices and distances from data matrix
g <- add_edges(make_empty_graph(n = 11, directed = FALSE), 
               t(seer[, 1:2])) %>%

  # Set vertice/node names 
  set_vertex_attr("name", value = c("NY","JF","DS","LG","LA","KS","LZ","NK","NN","NC","KC"))

# Set coordinates so looks similar to book diagram
  ## This is just for visualization, but could include it in data file
g$layout <- matrix(c(0,   0,   150, 150, 150, 170, 170, 170,  250, 250, 250,
                     150, 100, 200, 170, 140, 110,  80,  50,  180, 120, 60), nc = 2)

# Lable edges with the distance or weight
# E(g)$label <- seer[, 3]

```



```{r}
# Show network graph
plot(g)

```


# Q2 Shortest Path


+ How can Gail McGovern and the IFRC most quickly move workers from the United States to each of the nine IFRC cities? 
+ How long will it take workers and supplies to reach each city using the quickest route? 
+ Which routes appear to have significant time bottlenecks that the IFRC should work to reduce? 
+ Provide a table and/or network map indicating the quickest route and travel time between the United States and African cities on the network.



```{r}
# Data matrix, could also import data file
seer <- matrix(nc = 3, byrow = TRUE, 
              c(1, 4, 172,
                1, 5, 186,
                1, 6, 18,
                2, 3, 112,
                2, 7, 20,
                2, 8, 20,
                6, 9, 5,
                6, 10, 2,
                7, 11, 3)) 
 

# Make graph by setting 11 nodes/vertices, edges from nodes/vertices and distances from data matrix
g <- add_edges(make_empty_graph(n = 11, directed = FALSE), 
               t(seer[, 1:2]), weight=seer[,3]) %>%
  
  # Set vertice/node names 
  set_vertex_attr("name", value = c("NY","JF","DS","LG","LA","KS","LZ","NK","NN","KC","NC"))

# Set coordinates so looks similar to book diagram
  ## This is just for visualization, but could include it in data file
g$layout <- matrix(c(0,   0,   150, 150, 150, 170, 170, 170,  250, 250, 250,
                     150, 100, 200, 170, 140, 110,  80,  50,  180, 120, 60), nc = 2)

# Lable edges with the distance or weight
E(g)$label <- seer[, 3]
#E(g)$label.cex <- 0.5

# Show network graph
plot(g)

```


```{r}
# Show network graph
plot(g)

```

# Q3 Minimum Cost

+ How should the IFRC satisfy each African city’s need requirements at minimum cost? 
+ Again, where are the significant bottlenecks in the system that the IFRC should work to reduce? 
+ Provide a table and/or network map highlighting the least cost route between the U.S. and African cities.

```{r echo = FALSE, include = FALSE}
# Set up model
mc <- make.lp(0, 27)

# Set objective fn 
obj_fn <- c(32, 30, 30, 45, 50, 55, 56, 48, 44, 49, 57, 61, 5, 9, 4, 7, 5, 8, 22, 19, 4, 24, 22, 23, 28, 25, 2)
set.objfn(mc, obj_fn)

# Run as min
lp.control(mc, sense = "min")

# Add constraints
add.constraint(mc, c( 1, 1, 1, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "=", 500000) #NY output
add.constraint(mc, c( 0, 0, 0, 0, 0, 0, 1, 1, 1, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "=", 500000) #JF output
add.constraint(mc, c( -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "=", -50000) #DS demand
add.constraint(mc, c( 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "=", -100000) #LG demand
add.constraint(mc, c( 0, 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0), "=", -130000) #LA demand
add.constraint(mc, c( 0, 0, 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1, 0, 0, 0, 0, 0, 0), "=", -90000) #KS demand
add.constraint(mc, c( 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1, 0, 0, 0), "=", -150000) #LZ demand
add.constraint(mc, c( 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1), "=", -120000) #NK demand
add.constraint(mc, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 0, 0, -1, 0, 0, -1, 0, 0), "=", -100000) #NN demand
add.constraint(mc, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 0, -1, 0, -1, 0, 0, -1, 0, 0, -1, 0, 0, -1, 0), "=", -180000) #KC demand
add.constraint(mc, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 0, -1, 0, -1, 0, 0, -1, 0, 0, -1, 0, 0, -1), "=", -80000) #NC demand

add.constraint(mc, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 14868) #DS-NC truck restriction 840 * 17.7
add.constraint(mc, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 14868) #LG-NC truck restriction 840 * 17.7
add.constraint(mc, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 14868) #LA-NC truck restriction 840 * 17.7
add.constraint(mc, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0), "<=", 30000) #KS-NC air restriction 200 * 150
add.constraint(mc, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0), "<=", 30000) #LZ-NC air restriction 200 * 150

# Add names
dimnames(mc) <- list(c("NY", "JF","DS", "LG", "LA", "KS", "LZ", "NK", "NN", "KC", "NC", "U(DS-NC)", "U(LG-NC)", "U(LA-NC)", "U(KS-NC)", "U(LZ-NC)"), 
                      c("NY-DS", "NY-LG", "NY-LA", "NY-KS", "NY-LZ", "NY-NK", "JF-DS", "JF-LG", "JF-LA", "JF-KS", "JF-LZ", "JF-NK", "DS-KC", "DS-NC", "LG-KC", "LG-NC", "LA-KC", "LA-NC", "KS-NN", "KS-KC", "KS-NC", "LZ-NN", "LZ-KC", "LZ-NC", "NK-NN", "NK-KC", "NK-NC"))

# Write to view the algebraic formulation
write.lp(mc, "mc.lp",type = 'lp')

# Solve the model
solve(mc)
```


```{r echo = FALSE, include = FALSE}
# Make solution/sensitivity analysis table
# Get primal solution
ps <- get.primal.solution(mc)

# Have to re-enter obj fn to get Sens Ana table since cannot pull from model
obj_fn <- c(32, 30, 30, 45, 50, 55, 56, 48, 44, 49, 57, 61, 5, 9, 4, 7, 5, 8, 22, 19, 4, 24, 22, 23, 28, 25, 2)

# Get sensitivity analysis
obj_sa <- get.sensitivity.obj(mc)
rhs_sa <- get.sensitivity.rhs(mc)

n <- length(get.variables(mc))
m <- length(get.constr.type(mc))
ov <- paste0("Objective Value = ", ps[1])

sa_tab <- rbind(ps[2:(n + m + 1)], 
                c(round(rhs_sa$duals[1:m], 2), obj_fn),
                round(c(rhs_sa$dualsfrom[1:m],obj_sa$objfrom), 2),
                round(c(rhs_sa$dualstill[1:m],obj_sa$objtill), 2)) 
colnames(sa_tab) <- c(rownames(mc), colnames(mc))
rownames(sa_tab) <- c("solution", "duals/coef", "Sens From", "Sens Till")      

# Substitute "inf" and "-inf" so tables are easier to read (coded by two classmates!)
sa_tab <- ifelse(sa_tab == -1.000e+30, "-inf", sa_tab)
sa_tab <- ifelse(sa_tab == 1.000e+30, "inf", sa_tab)

```

```{r echo = FALSE}
# Print the table
kable(sa_tab, format.args = list(big.mark = ",")) %>%
  kable_styling(bootstrap_options = c("striped", "bordered")) %>% 
  add_footnote(label = ov, notation = "none")

```

```{r}
# Set up model
sp <- make.lp(0, 30)



# Set objective fn and constraints

obj_fn <- c(32, 30, 30, 45, 50, 55, 56, 48, 44, 49, 57, 61, 5, 5, 9, 3, 4, 7, 3, 5, 8, 22, 19, 4, 24, 22, 23, 28, 25, 2)
set.objfn(sp, obj_fn)

# Add and constraints

add.constraint(sp, c( 240, 240, 240, 150, 150, 150, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "=", 500000) #NY
add.constraint(sp, c( 0, 0, 0, 0, 0, 0, 240, 240, 240, 150, 150, 150, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "=", 500000) #JF
add.constraint(sp, c( -240, 0, 0, 0, 0, 0, -240, 0, 0, 0, 0, 0, 17.7, 17.7, 17.7, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "=", -50000) #DS
add.constraint(sp, c( 0, -240, 0, 0, 0, 0, 0, -240, 0, 0, 0, 0, 0, 0, 0, 17.7, 17.7, 17.7, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "=", -100000) #LG
add.constraint(sp, c( 0, 0, -240, 0, 0, 0, 0, 0, -240, 0, 0, 0, 0, 0, 0, 0, 0, 0, 17.7, 17.7, 17.7, 0, 0, 0, 0, 0, 0, 0, 0, 0), "=", -130000) #LA
add.constraint(sp, c( 0, 0, 0, -150, 0, 0, 0, 0, 0, -150, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 150, 150, 150, 0, 0, 0, 0, 0, 0), "=", -90000) #KS
add.constraint(sp, c( 0, 0, 0, 0, -150, 0, 0, 0, 0, 0, -150, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  150, 150, 150, 0, 0, 0), "=", -150000) #LZ
add.constraint(sp, c( 0, 0, 0, 0, 0, -150, 0, 0, 0, 0, 0, -150, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  150, 150, 150), "=", -120000) #NK
add.constraint(sp, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -17.7, 0, 0, -17.7, 0, 0, -17.7, 0, 0, -150, 0, 0, -150, 0, 0, -150, 0, 0), "=", -100000) #NN
add.constraint(sp, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -17.7, 0, 0, -17.7, 0, 0, -17.7, 0, 0, -150, 0, 0, -150, 0, 0, -150, 0), "=", -180000) #KC
add.constraint(sp, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -17.7, 0, 0, -17.7, 0, 0, -17.7, 0, 0, -150, 0, 0, -150, 0, 0, -150), "=", -80000) #NC
add.constraint(sp, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 0) # DS NN 0
add.constraint(sp, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 0) # LG NN 0
add.constraint(sp, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 0) # LA NN 0
add.constraint(sp, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 840) # DS NC 17.7 *840
add.constraint(sp, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 840) # LG NC
add.constraint(sp, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 840) # LA NC
add.constraint(sp, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0), "<=", 200) # KS NC 150*200
add.constraint(sp, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0), "<=", 200) # LZ NC


# Add names
dimnames(sp) <- list(c("NY", "JF","DS", "LG", "LA", "KS", "LZ", "NK", "NN", "KC", "NC", "UDS-NN", "ULG-NN", "ULA_NN", "UDS-NC","ULG-NC","ULA-NC","UKS-NC","ULZ-NC"), 
                      c("NY-DS", "NY-LG", "NY-LA", "NY-KS", "NY-LZ", "NY-NK", "JF-DS", "JF-LG", "JF-LA", "JF-KS", "JF-LZ", "JF-NK", "DS-NN", "DS-KC", "DS-NC", "LG-NN", "LG-KC", "LG-NC", "LA-NN", "LA-KC", "LA-NC", "KS-NN", "KS-KC", "KS-NC", "LZ-NN", "LZ-KC", "LZ-NC", "NK-NN", "NK-KC", "NK-NC"))

# Write to view the algebraic formulation
write.lp(sp, "sp30-1.lp",type = 'lp')

# Solve the model
solve(sp)
```

```{r echo = FALSE, include = FALSE}
# Make results and sensitivity table 
ps <- get.primal.solution(sp)
obj_sa <- get.sensitivity.obj(sp)
rhs_sa <- get.sensitivity.rhs(sp)

nv <- length(get.variables(sp))
mc <- length(get.constr.type(sp))
ov <- paste0("Objective Value = ", ps[1])

sa_tab <- rbind(round(ps[2:(nv + mc + 1)], 2), 
                round(c(rhs_sa$duals[1:mc], obj_fn), 2),
                round(c(rhs_sa$dualsfrom[1:mc],obj_sa$objfrom), 2),
                round(c(rhs_sa$dualstill[1:mc],obj_sa$objtill), 2)) 
colnames(sa_tab) <- c(rownames(sp), colnames(sp))
rownames(sa_tab) <- c("solution", "duals/coef", "Sens From", "Sens Till")      

# Substitute "inf" and "-inf" so tables are easier to read (coded by two classmates!)
sa_tab <- ifelse(sa_tab == -1.000e+30, "-inf", sa_tab)
sa_tab <- ifelse(sa_tab == 1.000e+30, "inf", sa_tab)

```


```{r echo = FALSE}
# Print the table
knitr::kable(sa_tab, format.args = list(big.mark = ",")) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "bordered")) %>% 
  kableExtra::add_footnote(label = ov, notation = "none")

```


# Q4 Max Flow

+ How can the IFRC maximize the total amount of cargo that reaches Africa?
+ Again, where are the significant bottlenecks in the system that the IFRC should work to reduce?
+ Provide a table and/or network map highlighting the maximum cargo and routes between the U.S. and African cities.


```{r echo = FALSE, include = FALSE}
# Set up model
mf <- make.lp(0, 30)

# Set objective fn 
obj_fn <- c(1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1)
set.objfn(mf, obj_fn)

# Run as max
lp.control(mf, sense = "max")

# Add constraints
add.constraint(mf, c( 1, 1, 1, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 500000) #NY output
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 1, 1, 1, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 500000) #JF output
add.constraint(mf, c( -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ">=", -50000) #DS demand
add.constraint(mf, c( 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ">=", -100000) #LG demand
add.constraint(mf, c( 0, 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0), ">=", -130000) #LA demand
add.constraint(mf, c( 0, 0, 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1, 0, 0, 0, 0, 0, 0), ">=", -90000) #KS demand
add.constraint(mf, c( 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1, 0, 0, 0), ">=", -150000) #LZ demand
add.constraint(mf, c( 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1), ">=", -120000) #NK demand
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 0, 0, -1, 0, 0, -1, 0, 0, -1, 0, 0, -1, 0, 0, -1, 0, 0), ">=", -100000) #NN demand
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 0, 0, -1, 0, 0, -1, 0, 0, -1, 0, 0, -1, 0, 0, -1, 0), ">=", -180000) #KC demand
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 0, 0, -1, 0, 0, -1, 0, 0, -1, 0, 0, -1, 0, 0, -1), ">=", -80000) #NC demand

add.constraint(mf, c( 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 75000) #NY-KS air restriction 500 * 150
add.constraint(mf, c( 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 45000) #NY-LZ air restriction 300 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 75000) #NY-NK air restriction 500 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 90000) #JF-KS air restriction 600 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 75000) #JF-LZ air restriction 500 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 105000) #JF-NK air restriction 700 * 150

add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 13452) #DS-KC Truck restriction 760 * 17.7
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 7965) #DS-NC truck restriction 450* 17.7
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 5310) #LG-KC truck restriction 300 * 17.7
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 2832) #LG-NC truck restriction 160 * 17.7
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 4425) #LA-KC truck restriction 250 * 17.7
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 4248) #LA-NC truck restriction 240 * 17.7

add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 45000) #KS-NN air restriction 300 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0), "<=", 12000) #KS-KC air restriction 80 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0), "<=", 6000) #KS-NC air restriction 40 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0), "<=", 30000) #LZ-NN air restriction 200 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0), "<=", 21000) #LZ-KC air restriction 140 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0), "<=", 0) #LZ-NC air restriction 0 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0), "<=", 0) #NK-NN air restriction 0 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0), "<=", 6000) #NK-KC air restriction 40 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1), "<=", 45000) #NK-NC air restriction 300 * 150


# Add names
dimnames(mf) <- list(c("NY", "JF","DS", "LG", "LA", "KS", "LZ", "NK", "NN", "KC", "NC", "U(NY-KS)", "U(NY-LZ)", "U(NY-NK)", "U(JF-KS)", "U(JF-LZ)", "U(JF-NK)", "U(DS-KC)", "U(DS-NC)", "U(LG-KC)", "U(LG-NC)", "U(LA-KC)", "U(LA-NC)", "U(KS-NN)", "U(KS-KC)", "U(KS-NC)", "U(LZ-NN)", "U(LZ-KC)", "U(LZ-NC)", "U(NK-NN)", "U(NK-KC)", "U(NK-NC)"), 
                      c("NY-DS", "NY-LG", "NY-LA", "NY-KS", "NY-LZ", "NY-NK", "JF-DS", "JF-LG", "JF-LA", "JF-KS", "JF-LZ", "JF-NK", "DS-NN", "DS-KC", "DS-NC", "LG-NN", "LG-KC", "LG-NC", "LA-NN", "LA-KC", "LA-NC", "KS-NN", "KS-KC", "KS-NC", "LZ-NN", "LZ-KC", "LZ-NC", "NK-NN", "NK-KC", "NK-NC"))

# Write to view the algebraic formulation
#write.lp(mf, "mf.lp",type = 'lp')

# Solve the model
solve(mf)
```


```{r echo = FALSE, include = FALSE}
# Make solution/sensitivity analysis table
# Get primal solution
ps <- get.primal.solution(mf)

# Have to re-enter obj fn to get Sens Ana table since cannot pull from model
obj_fn <- c(1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1)

# Get sensitivity analysis
obj_sa <- get.sensitivity.obj(mf)
rhs_sa <- get.sensitivity.rhs(mf)

n <- length(get.variables(mf))
m <- length(get.constr.type(mf))
ov <- paste0("Objective Value = ", ps[1])

sa_tab <- rbind(ps[2:(n + m + 1)], 
                c(round(rhs_sa$duals[1:m], 2), obj_fn),
                round(c(rhs_sa$dualsfrom[1:m],obj_sa$objfrom), 2),
                round(c(rhs_sa$dualstill[1:m],obj_sa$objtill), 2)) 
colnames(sa_tab) <- c(rownames(mf), colnames(mf))
rownames(sa_tab) <- c("solution", "duals/coef", "Sens From", "Sens Till")      

# Substitute "inf" and "-inf" so tables are easier to read (coded by two classmates!)
sa_tab <- ifelse(sa_tab == -1.000e+30, "-inf", sa_tab)
sa_tab <- ifelse(sa_tab == 1.000e+30, "inf", sa_tab)

```

```{r echo = FALSE}
# Print the table
kable(sa_tab, format.args = list(big.mark = ",")) %>%
  kable_styling(bootstrap_options = c("striped", "bordered")) %>% 
  add_footnote(label = ov, notation = "none")

```


```{r echo = FALSE, include = FALSE}
# Set up model
mf <- make.lp(0, 27)

# Set objective fn 
obj_fn <- c(1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1)
set.objfn(mf, obj_fn)

# Run as max
lp.control(mf, sense = "max")

# Add constraints
add.constraint(mf, c( 1, 1, 1, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 500000) #NY output
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 1, 1, 1, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 500000) #JF output
add.constraint(mf, c( -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ">=", -50000) #DS demand
add.constraint(mf, c( 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ">=", -100000) #LG demand
add.constraint(mf, c( 0, 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0), ">=", -130000) #LA demand
add.constraint(mf, c( 0, 0, 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1, 0, 0, 0, 0, 0, 0), ">=", -90000) #KS demand
add.constraint(mf, c( 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1, 0, 0, 0), ">=", -150000) #LZ demand
add.constraint(mf, c( 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1), ">=", -120000) #NK demand
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 0, 0, -1, 0, 0, -1, 0, 0), ">=", -100000) #NN demand
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 0, -1, 0, -1, 0, 0, -1, 0, 0, -1, 0, 0, -1, 0), ">=", -180000) #KC demand
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 0, -1, 0, -1, 0, 0, -1, 0, 0, -1, 0, 0, -1), ">=", -80000) #NC demand

add.constraint(mf, c( 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 75000) #NY-KS air restriction 500 * 150
add.constraint(mf, c( 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 45000) #NY-LZ air restriction 300 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 75000) #NY-NK air restriction 500 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 90000) #JF-KS air restriction 600 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 75000) #JF-LZ air restriction 500 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 105000) #JF-NK air restriction 700 * 150

add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 13452) #DS-KC Truck restriction 760 * 17.7
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 7965) #DS-NC truck restriction 450* 17.7
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 5310) #LG-KC truck restriction 300 * 17.7
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 2832) #LG-NC truck restriction 160 * 17.7
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 4425) #LA-KC truck restriction 250 * 17.7
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 4248) #LA-NC truck restriction 240 * 17.7

add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 45000) #KS-NN air restriction 300 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0), "<=", 12000) #KS-KC air restriction 80 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0), "<=", 6000) #KS-NC air restriction 40 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0), "<=", 30000) #LZ-NN air restriction 200 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0), "<=", 21000) #LZ-KC air restriction 140 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0), "<=", 0) #LZ-NC air restriction 0 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0), "<=", 0) #NK-NN air restriction 0 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0), "<=", 6000) #NK-KC air restriction 40 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1), "<=", 45000) #NK-NC air restriction 300 * 150


# Add names
dimnames(mf) <- list(c("NY", "JF","DS", "LG", "LA", "KS", "LZ", "NK", "NN", "KC", "NC", "U(NY-KS)", "U(NY-LZ)", "U(NY-NK)", "U(JF-KS)", "U(JF-LZ)", "U(JF-NK)", "U(DS-KC)", "U(DS-NC)", "U(LG-KC)", "U(LG-NC)", "U(LA-KC)", "U(LA-NC)", "U(KS-NN)", "U(KS-KC)", "U(KS-NC)", "U(LZ-NN)", "U(LZ-KC)", "U(LZ-NC)", "U(NK-NN)", "U(NK-KC)", "U(NK-NC)"), 
                      c("NY-DS", "NY-LG", "NY-LA", "NY-KS", "NY-LZ", "NY-NK", "JF-DS", "JF-LG", "JF-LA", "JF-KS", "JF-LZ", "JF-NK", "DS-KC", "DS-NC", "LG-KC", "LG-NC", "LA-KC", "LA-NC", "KS-NN", "KS-KC", "KS-NC", "LZ-NN", "LZ-KC", "LZ-NC", "NK-NN", "NK-KC", "NK-NC"))

# Write to view the algebraic formulation
#write.lp(mf, "mf.lp",type = 'lp')

# Solve the model
solve(mf)
```


```{r echo = FALSE, include = FALSE}
# Make solution/sensitivity analysis table
# Get primal solution
ps <- get.primal.solution(mf)

# Have to re-enter obj fn to get Sens Ana table since cannot pull from model
obj_fn <- c(1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1)

# Get sensitivity analysis
obj_sa <- get.sensitivity.obj(mf)
rhs_sa <- get.sensitivity.rhs(mf)

n <- length(get.variables(mf))
m <- length(get.constr.type(mf))
ov <- paste0("Objective Value = ", ps[1])

sa_tab <- rbind(ps[2:(n + m + 1)], 
                c(round(rhs_sa$duals[1:m], 2), obj_fn),
                round(c(rhs_sa$dualsfrom[1:m],obj_sa$objfrom), 2),
                round(c(rhs_sa$dualstill[1:m],obj_sa$objtill), 2)) 
colnames(sa_tab) <- c(rownames(mf), colnames(mf))
rownames(sa_tab) <- c("solution", "duals/coef", "Sens From", "Sens Till")      

# Substitute "inf" and "-inf" so tables are easier to read (coded by two classmates!)
sa_tab <- ifelse(sa_tab == -1.000e+30, "-inf", sa_tab)
sa_tab <- ifelse(sa_tab == 1.000e+30, "inf", sa_tab)

```

```{r echo = FALSE}
# Print the table
kable(sa_tab, format.args = list(big.mark = ",")) %>%
  kable_styling(bootstrap_options = c("striped", "bordered")) %>% 
  add_footnote(label = ov, notation = "none")

```


```{r echo = FALSE, include = FALSE}
# Set up model
mf <- make.lp(0, 30)

# Set objective fn 
obj_fn <- c(1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1)
set.objfn(mf, obj_fn)

# Run as max
lp.control(mf, sense = "max")

# Add constraints
add.constraint(mf, c( 1, 1, 1, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 500000) #NY output
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 1, 1, 1, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 500000) #JF output
add.constraint(mf, c( -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ">=", -50000) #DS demand
add.constraint(mf, c( 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ">=", -100000) #LG demand
add.constraint(mf, c( 0, 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0), ">=", -130000) #LA demand
add.constraint(mf, c( 0, 0, 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1, 0, 0, 0, 0, 0, 0), ">=", -90000) #KS demand
add.constraint(mf, c( 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1, 0, 0, 0), ">=", -150000) #LZ demand
add.constraint(mf, c( 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1), ">=", -120000) #NK demand
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 0, 0, -1, 0, 0, -1, 0, 0, -1, 0, 0, -1, 0, 0, -1, 0, 0), ">=", -100000) #NN demand
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 0, 0, -1, 0, 0, -1, 0, 0, -1, 0, 0, -1, 0, 0, -1, 0), ">=", -180000) #KC demand
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 0, 0, -1, 0, 0, -1, 0, 0, -1, 0, 0, -1, 0, 0, -1), ">=", -80000) #NC demand

add.constraint(mf, c( 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 500 * 150) #NY-KS air restriction 500 * 150
add.constraint(mf, c( 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 300 * 150) #NY-LZ air restriction 300 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 500 * 150) #NY-NK air restriction 500 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 600 * 150) #JF-KS air restriction 600 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 500 * 150) #JF-LZ air restriction 500 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 700 * 150) #JF-NK air restriction 700 * 150

add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 700 * 17.7) #DS-KC Truck restriction 700 * 17.7
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 450* 17.7) #DS-NC truck restriction 450* 17.7
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 300 * 17.7) #LG-KC truck restriction 300 * 17.7
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 160 * 17.7) #LG-NC truck restriction 160 * 17.7
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 250 * 17.7) #LA-KC truck restriction 250 * 17.7
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 240 * 17.7) #LA-NC truck restriction 240 * 17.7

add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0), "<=", 300 * 150) #KS-NN air restriction 300 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0), "<=", 80 * 150) #KS-KC air restriction 80 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0), "<=", 40 * 150) #KS-NC air restriction 40 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0), "<=", 200 * 150) #LZ-NN air restriction 200 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0), "<=", 140 * 150) #LZ-KC air restriction 140 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0), "<=", 0) #LZ-NC air restriction 0 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0), "<=", 0) #NK-NN air restriction 0 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0), "<=", 40 * 150) #NK-KC air restriction 40 * 150
add.constraint(mf, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1), "<=", 300 * 150) #NK-NC air restriction 300 * 150


# Add names
dimnames(mf) <- list(c("NY", "JF","DS", "LG", "LA", "KS", "LZ", "NK", "NN", "KC", "NC", "U(NY-KS)", "U(NY-LZ)", "U(NY-NK)", "U(JF-KS)", "U(JF-LZ)", "U(JF-NK)", "U(DS-KC)", "U(DS-NC)", "U(LG-KC)", "U(LG-NC)", "U(LA-KC)", "U(LA-NC)", "U(KS-NN)", "U(KS-KC)", "U(KS-NC)", "U(LZ-NN)", "U(LZ-KC)", "U(LZ-NC)", "U(NK-NN)", "U(NK-KC)", "U(NK-NC)"), 
                      c("NY-DS", "NY-LG", "NY-LA", "NY-KS", "NY-LZ", "NY-NK", "JF-DS", "JF-LG", "JF-LA", "JF-KS", "JF-LZ", "JF-NK", "DS-NN", "DS-KC", "DS-NC", "LG-NN", "LG-KC", "LG-NC", "LA-NN", "LA-KC", "LA-NC", "KS-NN", "KS-KC", "KS-NC", "LZ-NN", "LZ-KC", "LZ-NC", "NK-NN", "NK-KC", "NK-NC"))

# Write to view the algebraic formulation
#write.lp(mf, "mf.lp",type = 'lp')

# Solve the model
solve(mf)
```



```{r echo = FALSE, include = FALSE}
# Make solution/sensitivity analysis table
# Get primal solution
ps <- get.primal.solution(mf)

# Have to re-enter obj fn to get Sens Ana table since cannot pull from model
obj_fn <- c(1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1)

# Get sensitivity analysis
obj_sa <- get.sensitivity.obj(mf)
rhs_sa <- get.sensitivity.rhs(mf)

n <- length(get.variables(mf))
m <- length(get.constr.type(mf))
ov <- paste0("Objective Value = ", ps[1])

sa_tab <- rbind(ps[2:(n + m + 1)], 
                c(round(rhs_sa$duals[1:m], 2), obj_fn),
                round(c(rhs_sa$dualsfrom[1:m],obj_sa$objfrom), 2),
                round(c(rhs_sa$dualstill[1:m],obj_sa$objtill), 2)) 
colnames(sa_tab) <- c(rownames(mf), colnames(mf))
rownames(sa_tab) <- c("solution", "duals/coef", "Sens From", "Sens Till")      

# Substitute "inf" and "-inf" so tables are easier to read (coded by two classmates!)
sa_tab <- ifelse(sa_tab == -1.000e+30, "-inf", sa_tab)
sa_tab <- ifelse(sa_tab == 1.000e+30, "inf", sa_tab)

```

```{r echo = FALSE}
# Print the table
kable(sa_tab, format.args = list(big.mark = ",")) %>%
  kable_styling(bootstrap_options = c("striped", "bordered")) %>% 
  add_footnote(label = ov, notation = "none")

```


```{r echo = FALSE, include = FALSE}
# Make solution/sensitivity analysis table
# Get primal solution
ps <- get.primal.solution(mf)

# Have to re-enter obj fn to get Sens Ana table since cannot pull from model
obj_fn <- c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1)

# Get sensitivity analysis
obj_sa <- get.sensitivity.obj(mf)
rhs_sa <- get.sensitivity.rhs(mf)

n <- length(get.variables(mf))
m <- length(get.constr.type(mf))
ov <- paste0("Objective Value = ", ps[1])

sa_tab <- rbind(ps[2:(n + m + 1)], 
                c(round(rhs_sa$duals[1:m], 2), obj_fn),
                round(c(rhs_sa$dualsfrom[1:m],obj_sa$objfrom), 2),
                round(c(rhs_sa$dualstill[1:m],obj_sa$objtill), 2)) 
colnames(sa_tab) <- c(rownames(mf), colnames(mf))
rownames(sa_tab) <- c("solution", "duals/coef", "Sens From", "Sens Till")      

# Substitute "inf" and "-inf" so tables are easier to read (coded by two classmates!)
sa_tab <- ifelse(sa_tab == -1.000e+30, "-inf", sa_tab)
sa_tab <- ifelse(sa_tab == 1.000e+30, "inf", sa_tab)

```

```{r echo = FALSE}
# Print the table
kable(sa_tab, format.args = list(big.mark = ",")) %>%
  kable_styling(bootstrap_options = c("striped", "bordered")) %>% 
  add_footnote(label = ov, notation = "none")

```








